Software Citation Principles

### 2016-03-22 sc-principles/software-citation-principles.tex
changed it's to it is in subsection 5.2
added Comput Phys Comm to subsection 4.2

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., Transactions on Mathematical Software [TOMS], Bioinformatics, F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals~\cite{aas-sofware-papers}. 
Professional societies are in a good position to change their respective communities, as the publishers of journals and conveners of domain-specific conferences; as publishers they can change editorial policies (as AAS has done) and conferences are an opportunity to communicate and discuss these changes with their communities.

@@

Currently, and for the foreseeable future, software papers are being published and cited,
in addition to software itself being cited, as many community norms and practices are
oriented towards citation of papers.
Given a software paper and software, the question of which should be cited and when is
complicated, and there is no simple answer.
As discussed in the Importance principle (\ref{principle:importance}), \textit{the software
itself should also be cited if it is directly used and was important to the work}.
If a software paper exists and it contains results (performance, validation, etc.) that are
important to the work, then the software paper should also be cited.
In addition, if the software authors ask that a paper should be cited, that should be respected.
Note that there are situations where it's appropriate to cite the software, the software paper, or both.

>>>>

One approach to increasing the `citability' of software is to encourage the
submission of papers in standard journals describing a piece of research
software, often known as software papers (see \S\ref{sec:software_papers}).
While some journals (e.g., Transactions on Mathematical Software [TOMS], Bioinformatics, Computer Physics Communications, F1000Research) have traditionally accepted
software submissions, the American Astronomical Society (AAS) have recently
announced they will accept software papers in their journals~\cite{aas-sofware-papers}. 
Professional societies are in a good position to change their respective communities, as the publishers of journals and conveners of domain-specific conferences; as publishers they can change editorial policies (as AAS has done) and conferences are an opportunity to communicate and discuss these changes with their communities.

@@

Currently, and for the foreseeable future, software papers are being published and cited,
in addition to software itself being cited, as many community norms and practices are
oriented towards citation of papers.
Given a software paper and software, the question of which should be cited and when is
complicated, and there is no simple answer.
As discussed in the Importance principle (\ref{principle:importance}), \textit{the software
itself should also be cited if it is directly used and was important to the work}.
If a software paper exists and it contains results (performance, validation, etc.) that are
important to the work, then the software paper should also be cited.
In addition, if the software authors ask that a paper should be cited, that should be respected.
Note that there are situations where it is appropriate to cite the software, the software paper, or both.
